Transient dynamics of granular slopes: continuum v discrete modelling

### 2016-07-14 paper.tex
MPM initial configuration

\Cref{fig:mpm_gradvelocity_200j} shows the initial evolution of the 
granular slope subjected to an initial horizontal energy $E_0 = 61$ (in 
dimensionless units) using MPM. As the granular slope is sheared along the 
bottom, the shear propagates to the top leaving a cavity in the vicinity of the 
left wall. This cavity gets partially filled as the granular mass at the top 
collapse behind the flowing mass due to inertia. Similar behaviour is observed 
during the initial stages of the flow evolution using DEM  
(\cref{fig:Gradient_Slope_CD_200J}). Due to inertia, the grains at the top 
of the granular heap roll down to fill the cavity, while the pile continues to 
spread.

\begin{figure}[tbph]
  \centering
  \begin{subfigure}[b]{0.47\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mpm_gradvelocity_200j}
    \caption{MPM}
    \label{fig:mpm_gradvelocity_200j}
  \end{subfigure}
  \begin{subfigure}[b]{0.47\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/Gradient_Slope_CD_200J}
    \caption{DEM}
    \label{fig:Gradient_Slope_CD_200J}
  \end{subfigure}
  \caption{Evolution of granular piles subjected to a gradient
    horizontal energy.}
  \label{fig:gradvelocity_200j}
\end{figure}

>>>>

\Cref{fig:mpm_gradvelocity_200j} shows the initial evolution of the 
granular slope subjected to an initial horizontal energy $E_0 = 61$ (in 
dimensionless units) using MPM. As the granular slope is sheared along the 
bottom, the shear propagates to the top leaving a cavity in the vicinity of the 
left wall. This cavity gets partially filled as the granular mass at the top 
collapse behind the flowing mass due to inertia. Similar behaviour is observed 
during the initial stages of the flow evolution using DEM  
(\cref{fig:dem_gradvelocity_200j}). Due to inertia, the grains at the top 
of the granular heap roll down to fill the cavity, while the pile continues to 
spread.

\begin{figure}[tbph]
  \centering
  \begin{subfigure}[b]{0.47\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mpm_gradvelocity_200j}
    \caption{MPM}
    \label{fig:mpm_gradvelocity_200j}
  \end{subfigure}
  \begin{subfigure}[b]{0.42\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/dem_gradvelocity_200j}
    \caption{DEM}
    \label{fig:dem_gradvelocity_200j}
  \end{subfigure}
  \caption{Evolution of granular piles subjected to a gradient
    horizontal energy of 200J.}
  \label{fig:gradvelocity_200j}
\end{figure}
